Croder: Bringing the Knowledge of the Crowds into the IDE

### 2013-05-03 paper/paper.tex
Made the table nicer

% Load basic packages
\usepackage{balance}  % to better equalize the last page
\usepackage{graphics} % for EPS, load graphicx instead
\usepackage{times}    % comment if you want LaTeX's default font
\usepackage{url}      % llt: nicely formatted URLs
\usepackage{nameref}
\usepackage{xspace}

@@

\begin{table*}
	\begin{center}
	\begin{tabular}{| p{3cm} || p{4cm} | p{4cm} | p{4cm} |}
	\hline
	& Primary User & Secondary User & Tertiary User \\ \hline \hline
	\textbf{Pseudoname} & Ben & Kyle & Karla \\ \hline
	\textbf{Education} & PhD Student & MFA Graduate & MBA Student \\ \hline
	\textbf{Type} & Pragmatic & Opportunistic & Exploratory \\ \hline
	\textbf{Attitude} & Writes code methodically. Develops sufficient understanding of a technology
		to enable component use of it. Prides himself or herself to building robust application or
		technical challenges. & 
		Writes code in an exploratory fashion. Develops a fundamental
		understanding of a technology to understand how it can solve a specific problem &
		Barely write code all by herself. Develop with limited understanding of Java language 
		and she is having a trouble with developing her ideas with a basic syntax quite occasionally. \\ \hline
	\textbf{Motto} & I want to focus on creating something new while somebody cleans up my slight mistakes. &
		I sometimes feel dizzy because I can't find what is wrong with my code. &
		I barely started to write code in Java to prove my model in the class. But I don't know how to. \\ \hline
	\textbf{Computer literacy} & Expert. Majored in CS & Intermediate. Majored in Art and Design & Basic
		Majored in Business \\ \hline
	\textbf{Pair programming experience} & Java, C, C++, Matlab etc. & Adobe ActionScript, HTML/CSS,
		Proce55ing, Java & Visual Basic, Mathematica \\ \hline
	\textbf{Three Most frequent sites they use when they are programming} & GitHub, StackOverflow, Codeguru &
		Google, StackOverflow, Open Processing & Google, eHow, Quora \\ \hline
	\textbf{Goal} & Find related info; Find an optimized process or algorithm & Find related info; Find previous
		Q\&A that may help his problem & Find source code; Looking for someone who can answer her
		questions. \\ \hline
	\end{tabular}
	\end{center}
\caption{Persona table to show their situation, background and goal to code review}
\label{table:persona}
\end{table*}

>>>>

% Load basic packages
\usepackage{balance}  % to better equalize the last page
\usepackage{graphics} % for EPS, load graphicx instead
\usepackage{times}    % comment if you want LaTeX's default font
\usepackage{url}      % llt: nicely formatted URLs
\usepackage{nameref}
\usepackage{xspace}
\usepackage{array}

@@

\begin{table*}[hbt]
	\begin{center}
	\begin{tabular}{| m{3cm} || p{4cm} | p{4cm} | p{4cm} |}
	\hline
	& \begin{center}Primary User\end{center} & 
		\begin{center}Secondary User\end{center} & 
		\begin{center}Tertiary User\end{center} \\ \hline \hline
	\textbf{Pseudoname} & Ben & Kyle & Karla \\ \hline
	\textbf{Education} & PhD Student & MFA Graduate & MBA Student \\ \hline
	\textbf{Type} & Pragmatic & Opportunistic & Exploratory \\ \hline
	\textbf{Attitude} & Writes code methodically. Develops sufficient understanding of a technology
		to enable component use of it. Prides himself or herself to building robust application or
		technical challenges. & 
		Writes code in an exploratory fashion. Develops a fundamental
		understanding of a technology to understand how it can solve a specific problem &
		Barely write code all by herself. Develop with limited understanding of Java language 
		and she is having a trouble with developing her ideas with a basic syntax quite occasionally. \\ \hline
	\textbf{Motto} & I want to focus on creating something new while somebody cleans up my slight mistakes. &
		I sometimes feel dizzy because I can't find what is wrong with my code. &
		I barely started to write code in Java to prove my model in the class. But I don't know how to. \\ \hline
	\textbf{Computer literacy} & Expert. Majored in CS & Intermediate. Majored in Art and Design & Basic
		Majored in Business \\ \hline
	\textbf{Pair programming experience} & Java, C, C++, Matlab etc. & Adobe ActionScript, HTML/CSS,
		Proce55ing, Java & Visual Basic, Mathematica \\ \hline
	\textbf{Three most frequent sites they use when they are programming} & GitHub, StackOverflow, Codeguru &
		Google, StackOverflow, Open Processing & Google, eHow, Quora \\ \hline
	\textbf{Goal} & Find related info; Find an optimized process or algorithm & Find related info; Find previous
		Q\&A that may help his problem & Find source code; Looking for someone who can answer her
		questions. \\ \hline
	\end{tabular}
	\end{center}
\caption{Persona table to show their situation, background and goal to code review}
\label{table:persona}
\end{table*}
